Alleviating the Topology Mismatch Problem in Unstructured and Structured P2P Overlay Networks: A Survey

### 2014-01-23 unstructured.tex
2012.08.20 (Vassilis) Added LaTeX tables (known issue on wrapping text inside cells). Reshaped discussion material. Introducing rough, algorithm performance, estimation (high, medium, low) by tracking efficiency, control overhead and scalability. First attempt on plotting data in a systematic way (needs more work though).

%###############################################################################
%###############################################################################
%       BROADCAST OPTIMISATION
%###############################################################################
%###############################################################################

@@

% TODO: local indices is a cache based algorithm so maybe we have to put a
% reference to the respective section???
In local indices, as shown in Figure~\ref{figure:dbfs:localindx}, each node
indexes data within a radius of $r$ hops and uses this local index to answer
queries on behalf of them without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and improves query
efficiency, however, updating the indices in cases with frequent node joins and
leaves introduces a serious overhead to the system if the radius is kept broad.

@@

% TODO: from the following (commented out) design components of Gia has one
% part that falls into topology adaptation, one part on forwarding optimisation
% and one part on

@@

@@

%
% TODO: SOME DISCUSSION
%
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
%Experiments in \cite{zhu_dcmp_2008} showed that DCMP incurs a lower delay,
% returns more results and decreases the number of duplicate messages by 22\%,
%compared to LTM. Additionally DCMP has one to two orders of magnitude less
%overhead, because it adopts a more ``LAZY'' approach than broadcasting control
%messages periodically like LTM does.
%

%###############################################################################
%###############################################################################
%###############################################################################
%       CACHING
%###############################################################################
%###############################################################################
%###############################################################################

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{Cohen02} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyse the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed in this paper, which is a model between the
uniform and proportional allocation.  In order to evaluate the outcome of the
replication models, the overall costs of successful and unsuccessful searches in
the network are compared. Results argue that the uniform allocation model
minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
behave much better. Therefore they propose the square root allocation approach,
which is a replication strategy that minimizes the expected search size of
successful queries in P2P networks.

@@

%###############################################################################
%###############################################################################
%###############################################################################
%       OVERLAY OPTIMISATION
%###############################################################################
%###############################################################################
%###############################################################################

@@

\emph{Narada} \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada is considered pioneering
(maybe along with \emph{Scattercast} \cite{chawathe_scattercast_2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{li_enarada_2008} used Gossip protocol for the construction
}
as shown in Figure~\ref{figure:narada}. They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
imporpant limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004} builds an
overlay multicast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbour connections that are
not in that tree. To achieve that it calculate cost between nodes using network
delay as a metric. Each peer probes the costs with its immediate logical
neighbours and forms a \emph{neighbour cost table (NCT)} using a special
routing message type. Two neighbouring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbours forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbours is built. Ultimately, physically
far away neighbours are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbour's neighbour,
say $G$ and $H$ respectively. Assuming that the link to the neighbour's neigbour
($SH$) is smaller that that of the neighbour ($SG$), the later is cut and a new
connection is established. In the oposite situation where $SG$ is smaller than
$SH$ then if $SH$ is smaller that $GH$ then $H$ is preserved as $S$'s new
neighbour. In the case where $SH$ is larger than $SG$ and $GH$, no connection
will be established and $S$ will continue probing another neighbour's neighbour.
The above optimisation is conducted within $1$-neighbour closure (among its
source peer and all its direct neighbours) but the scope can be extended. The
larger the scope, the better topology matching improvement but also the greater
the computational overhead.

%
% TODO: SOME DISCUSSION
%
%Simulations in \cite{liu_acesims_2004} show that the average scope of each
% query to cover the same scope of nodes is reduced by about 65 percent without
%losing any autonomy feature, while the average response time can be reduced by
%35 percent. Larger diameter topologies lead to better topology optimization
%rate but also to higher communication and computation overhead. It was also
%found that it is more effective in higher connectivity dense topologies.
%Compared to LTM, it comes short of convergence speed. In
%\cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and
%response time (80 percent) to message queries without shrinking the search
%scope. SBO, on the other hand, achieves approximately 85 percent reduction on
%traffic cost and about 60 percent reduction on query response time. Last but
%not least, it is concluded that work must be done on incorporating a more
%sophisticated selection policy for candidate non-flooding peers.
%

@@

@@

@@

%
% TODO: SOME DISCUSSION
%
%In a static enviromnent LTM may reduce traffic cost by around 80 to 85 percent
% while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is
%proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM
%reduces response time by more than 60 percent in 3 steps while SBO needs 8. In
%a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each
%peer) SBO and LTM reduce the average traffic cost per query (including the
%overhead due to the optimization steps) by 85 and 80 percent, respectively.
%Moreover LTM reduces the response time per query to 30 percent while SBO to 35
%percent.
%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: DOUBLE CHECK IF THIS ALGORITHM GOES IN THIS SECTION/SUBSECTION
\subsubsection{Adaptive Peer Selection}
Bernstein et al., contributed on the use of machine learning for building peer
selection strategies from past experience \cite{bflz_adaptpeersel_2003}. A
decision tree is used to rate peers based on information about connection
characteristics that is collected. These can be load, bandwidth, and past
uploading experience. Then a by Markov decision process is incorporated as a
mechanism to shape the policy for switching among the peers. The problem
with this approach is that the peer selection algorithm is slow due to the
learning process and the complexity of the method.

@@

@@

% TODO: CHECK IF THE FOLLOWING BITTORRENT ALGORITMS BELONG IN THIS SUBSECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Biased Neighbour Selection}
Bindal et al. \cite{rpc_bitbiased_2006} claim to strengthen BitTorrent
protocol\cite{c_bittorrent_2003} locality by selecting most of a peer's
neighbours to be out of the same ISP, while preserving the near optimal download
performance of the protocol itself. BitTorrent systems employ most of the time
mechanisms that can be proven very aggresive to an ISP's networking and
accounting, basically, due to their lack of knowlegde of AS boarder limits.
BitTorrent specification, by default allows for each peer, 35 connections.
Biased neighbour selection experiments on some number $k$ which denotes a number
of neighbouring peers which are not on the same ISP than the peer at hand.
Consequently, the remaining $35 - k$ peers are from the same ISP. These $k$
nodes are used in order to preserve a more extended, global view of a network,
but in the same localize the load within the limits of a single ISP. This
prevents clients from exchanging traffic through an expensive transit link, if
there are alternative local connections that could offer the same, faster and at
no additional cost for the ISP. Implementation can either be done through
modifications on the tracker side, to identify ISP locallity, or through P2P
traffic shaping devices installed on ISP's edge routers. The paper also proposes
combination of biased neighbour selection along with bandwidth throttling and
some caching approach for near optimal results. Unfortunatelly, implementation
need, in some extend, contribution (exposure of ISP AS mappings) or
infrastructure changes (installation of P2P traffic shaping devices) on the ISP
level itself, making the adoption difficult in the general case.

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Underlying Topology-Aware Peer Selection (UTAPS)}
UTAPS \cite{lcy_utaps_2008} is another peer selection strategy for the
BitTorrent protocol. Its first step is to collect the needed information in
order to construct a picture of the underlying topology and the second is to
make the peer selection, per se, based on this knowledge. For the first part,
the algorithm uses network tomography, a technique which suggests probing only
from a large network's end points in order to infer its internal characteristics
\cite{chny_tomography_2002}. Upon a new peer arrival, the tracker traceroutes it
to get some knowledge (IP address, routers involved, RTT and hops conducted
e.t.c). The more the peers in the swarm the better picture a tracker has for the
underlying infrastructure, which can then return to the newcomming peer in the
form of the bootstrapping peer list. The peers furtherly enhance this picture by
tracerouting the returned peers themselves and reporting back to the tracker.
For the selection part, a family of heuristics are proposed, which in general
target those peers that expose low RTT and are within certain hop-count away of
measured routers. The author's claim that peers running UTAPS instead of random
peer selection can achieve better downloading rates with reduced burden on the
underlying ISP infrastructure though their technique is coarse-grained and their
evaluation configuration was far too small for extracting further safe
conclusions.

@@

@@

@@

@@

\subsubsection{Critical Topology-Aware Grouping (CTAG)}
\emph{Critical Topology-Aware Grouping (CTAG)} presented in
\cite{zhao_ctag_2006}, is a grouping algorithm. The grouping strategy is based
on the \emph{Internet Assigned Numbers Authority (IANA)} and the respective
\emph{Regionanal Internet Registry (RIR)}'s IP assignment strategies, according
to which nodes within the same organization are always addressed from the same
block. The paper proposes the \emph{Adjacency Measurement (AM)}, a technique
which uses the longest matching IP segment criterion to calculate node
proximity. CTAG focuses on both the construction of the overlay as well as its
constant and dynamic adaptation. In the first, called \emph{bootstrapping
grouping}, the \emph{Gnutella Web Caching} mechanism is modified in order for a
newcomer to choose the closest cache to retrieve the bootstrapping list. In the
second, called \emph{dynamic revision} in the paper's context, the AM metric is
used to store hosts' addresses. read from \emph{X-Try} headers during handshake
or from \emph{QueryHit} messages. Additionally, when a node reaches the max
neighbour connections, node disconnects the neighbours with the lowestAM.

>>>>

%       BROADCAST OPTIMISATION

@@

In local indices, as shown in Figure~\ref{figure:dbfs:localindx}, each node
indexes data within a radius of $r$ hops and uses this local index to answer
queries on behalf of them without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and improves query
efficiency, however, updating the indices in cases with frequent node joins and
leaves introduces a serious overhead to the system if the radius is kept broad.

% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the begining at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spirral).
medium &
% BFS is Gnutella's non efficient communcation method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated acros the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
\end{center}

@@

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Drastically reduces the search scope.
low &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them
low &
% Reduced search scope makes this not really scalable
low
\end{tabular}
\end{center}

@@

%
% TODO: SOME DISCUSSION
%
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It return more result than LTM according to experiments in
% \cite{zhu_dcmp_2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimises this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{zhu_dcmp_2008}
low &
% fully distributed method
high
\end{tabular}
\end{center}

%       CACHING

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Replication Strategies in Unstructured Peer-to-Peer Networks}
\cite{Cohen02} aim to improve the inefficient blind search algorithm by
replicating the data in a P2P network. The main intuition behind the
idea of replication, or using cached copies, is that as the number of copies for
each item increases in the network, it would be easier for a search algorithm,
even a random one, to locate these items. In order to analyse the feasibility of
such an approach, the authors investigate three different replication
strategies, namely uniform, proportional, and square root allocation. In the
uniform model, the copies of items are uniformly replicated in the network,
while in the proportional model, the items are replicated based on their query
rate, so that frequently queried items are replicated more. The square root
allocation is a strategy proposed in this paper, which is a model between the
uniform and proportional allocation.  In order to evaluate the outcome of the
replication models, the overall costs of successful and unsuccessful searches in
the network are compared. Results argue that the uniform allocation model
minimizes the maximum search size, therefore reduces the time spent on an
unsuccessful search. The proportional model, on the other hand, promotes the
more frequently queried items by replicating them more, therefore decreases the
search time for popular items, but suffers when needing to locate the rare
items. The authors also claim that the expected successful search size is the
same for uniform and proportional models, and any approach between them would
always behave much better. Therefore they propose the square root allocation
approach, which is a replication strategy that minimizes the expected search
size of successful queries in P2P networks.

\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimatelly got fulfilled
medium \\
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
? &
%
? &
%
?
\end{tabular}
\end{center}

%       OVERLAY OPTIMISATION

@@

\emph{Narada} \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada has been pioneering
(maybe along with \emph{Scattercast} \cite{chawathe_scattercast_2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{li_enarada_2008} used Gossip protocol for the construction
}
as shown in Figure~\ref{figure:narada}. They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
important limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
low &
% The overhead of Narada is proportional to the multicast group size
high &
%
low
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbours as well as between
% any pair of neighbours. Whenever a new neighbour cost table is received or
% there is a change of neighbours, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004} builds an
overlay multicast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbour connections that are
not in that tree. To achieve that it calculates cost between nodes using network
delay as a metric. Each peer probes the costs with its immediate logical
neighbours and forms a \emph{neighbour cost table (NCT)} using a special
routing message type. Two neighbouring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbours forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbours is built. Ultimately, physically
far away neighbours are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbour's neighbour,
say $G$ and $H$ respectively. Assuming that the link to the neighbour's neigbour
($SH$) is smaller that that of the neighbour ($SG$), the later is cut and a new
connection is established. In the oposite situation where $SG$ is smaller than
$SH$ then if $SH$ is smaller that $GH$ then $H$ is preserved as $S$'s new
neighbour. In the case where $SH$ is larger than $SG$ and $GH$, no connection
will be established and $S$ will continue probing another neighbour's neighbour.
The above optimisation is conducted within $1$-neighbour closure (among its
source peer and all its direct neighbours) but the scope can be extended. The
larger the scope, the better topology matching improvement but also the greater
the computational overhead.

%
% TODO: SOME DISCUSSION
%
%Simulations in \cite{liu_acesims_2004} show that the average scope of each
% query to cover the same scope of nodes is reduced by about 65 percent without
%losing any autonomy feature, while the average response time can be reduced by
%35 percent. Larger diameter topologies lead to better topology optimization
%rate but also to higher communication and computation overhead. It was also
%found that it is more effective in higher connectivity dense topologies.
%Compared to LTM, it comes short of convergence speed. In
%\cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and
%response time (80 percent) to message queries without shrinking the search
%scope.Last but
%not least, it is concluded that work must be done on incorporating a more
%sophisticated selection policy for candidate non-flooding peers.
%

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
high &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Authors claim 75% reduction on traffic cost and about 65% reduction on query
% response time.
medium &
%
medium &
%
medium
\end{tabular}
\end{center}

@@

%
% TODO: SOME DISCUSSION
%
%In a static enviromnent LTM may reduce traffic cost by around 80 to 85 percent
% while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is
%proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM
%reduces response time by more than 60 percent in 3 steps while SBO needs 8. In
%a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each
%peer) SBO and LTM reduce the average traffic cost per query (including the
%overhead due to the optimization steps) by 85 and 80 percent, respectively.
%Moreover LTM reduces the response time per query to 30 percent while SBO to 35
%percent.
%
%\cite{ni_mismatch_2004} shows SBO, achieves approximately 85 percent reduction
% on traffic cost and about 60 percent reduction on query response time.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% SBO reduces traffic cost between 85 and 90 percent
high &
% compared to LTM it has slower convergence speed thus incurres more, total,
% overhead.
medium &
%
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
medium &
% trivial overhead compared to the query cost savings and its convergent speed
% is faster than minimum spanning tree approaches so less overall overhead cost.
low &
% completely distributed and needs no global knowledge,
high
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% similar traffic reduction rate savings to LTM
medium &
% The traffic overhead of HAND is much less than that of LTM by an average of
% 55 percent.
low &
% no clock synching needed, fully distributed and with low control overhead the
% algorithm can be considered scalable.
high
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO: DOUBLE CHECK IF THIS ALGORITHM GOES IN THIS SECTION/SUBSECTION
\subsubsection{Adaptive Peer Selection (APS)}
Bernstein et al., contributed on the use of machine learning for building peer
selection strategies from past experience \cite{bflz_adaptpeersel_2003}. A
decision tree is used to rate peers based on information about connection
characteristics that is collected. These can be load, bandwidth, and past
uploading experience. Then a by Markov decision process is incorporated as a
mechanism to shape the policy for switching among the peers. The problem
with this approach is that the peer selection algorithm is slow due to the
learning process and the complexity of the method.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% machine learning the best way to adapt the overlay 
high &
% high computation overhead for learning and very slow convergence speed for
% the learning process.
high &
%
low
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% low clustering with larger coverage of peers with the same number of messages
% and reduced duplication.
medium &
% construction at peer join, while searching using local ``floods''
low &
% the selection of neighbours is done at join time. No overlay adaptation means
% low scalability in dynamic environments.
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% peer neighbourhood selected to minimise, for example, average delay
high &
% link state info (heartbeat) and delay estimation to all other nodes
% resulting to a complete picture of the overlay graph.
high &
% need global knowledge
low
\end{tabular}
\end{center}

% TODO: CHECK IF THE FOLLOWING BITTORRENT ALGORITMS BELONG IN THIS SUBSECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Biased Neighbour Selection (BNS)}
Bindal et al. \cite{rpc_bitbiased_2006} claim to strengthen BitTorrent
protocol\cite{c_bittorrent_2003} locality by selecting most of a peer's
neighbours to be out of the same ISP, while preserving the near optimal download
performance of the protocol itself. BitTorrent systems employ most of the time
mechanisms that can be proven very aggresive to an ISP's networking and
accounting, basically, due to their lack of knowlegde of AS boarder limits.
BitTorrent specification, by default allows for each peer, 35 connections.
Biased neighbour selection experiments on some number $k$ which denotes a number
of neighbouring peers which are not on the same ISP than the peer at hand.
Consequently, the remaining $35 - k$ peers are from the same ISP. These $k$
nodes are used in order to preserve a more extended, global view of a network,
but in the same localize the load within the limits of a single ISP. This
prevents clients from exchanging traffic through an expensive transit link, if
there are alternative local connections that could offer the same, faster and at
no additional cost for the ISP. Implementation can either be done through
modifications on the tracker side, to identify ISP locallity, or through P2P
traffic shaping devices installed on ISP's edge routers. The paper also proposes
combination of biased neighbour selection along with bandwidth throttling and
some caching approach for near optimal results. Unfortunatelly, implementation
need, in some extend, contribution (exposure of ISP AS mappings) or
infrastructure changes (installation of P2P traffic shaping devices) on the ISP
level itself, making the adoption difficult in the general case.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% inter-ISP cost minimised while retaining the near optimal performance of
% BitTorrent download.
high &
% this info is taken at swarm join
low &
% trackers should maintain and update proximity info/proximity info is
% retrieved from special hardware.
medium/high
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Authors claim minimisation of inter-ISP traffic cost while enhancing the,
% already, near optimal performance of BitTorrent download.
high &
% periodic DNS lookups and CDN redirection imposes medium control overhead to
% the method.
medium &
% the use of CDNs make the approach not fully distributed thus less scalable
low
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% minimisation of inter-AS traffic but unfair among peers.
medium &
% info (AS hop distances) aqcuired at swarm join
low &
%
high
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% it takes into account both dl speed and network topology. The later though is
% rathier coarse grained since it is taken into account on the AS level.
medium &
% the algoritm does not involve extensive calculations.
low &
% Does not need infrastructure and the calculations are distributed so it can
% scale
high
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Underlying Topology-Aware Peer Selection (UTAPS)}
UTAPS \cite{lcy_utaps_2008} is another peer selection strategy for the
BitTorrent protocol. Its first step is to collect the needed information in
order to construct a picture of the underlying topology and the second is to
make the peer selection, per se, based on this knowledge. For the first part,
the algorithm uses network tomography, a techni  que which suggests probing only
from a large network's end points in order to infer its internal characteristics
\cite{chny_tomography_2002}. Upon a new peer arrival, the tracker traceroutes it
to get some knowledge (IP address, routers involved, RTT and hops conducted
e.t.c). The more the peers in the swarm the better picture a tracker has for the
underlying infrastructure, which can then return to the newcomming peer in the
form of the bootstrapping peer list. The peers furtherly enhance this picture by
tracerouting the returned peers themselves and reporting back to the tracker.
For the selection part, a family of heuristics are proposed, which in general
target those peers that expose low RTT and are within certain hop-count away of
measured routers. The author's claim that peers running UTAPS instead of random
peer selection can achieve better downloading rates with reduced burden on the
underlying ISP infrastructure though their technique is coarse-grained and their
evaluation configuration was far too small for extracting further safe
conclusions.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% coarse grained approach of the network tomography doesn't provide a detailed
% picture of the underlying network that the peers can then exploit
medium &
% tracerout and hop counts and calculation from both the tracker and the peers
% (the later for all peers in the bootstrapping list) increases the control
% overhead of the approach.
medium &
%
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It incoorporates clustering of peers to inter- and intra ISP which is a
% rather coarse grained method.
medium &
% only on peer arrival proximities to routers are estimated and sent to the
% tracker. Even though the tracker is backing the identification of a peer
% being close or distant the actual computation is done in a distributed mannar
% thus not incurring too much additional controlling overhead.
medium &
% TODO: how intensive with regards to computing power is an online k-means (with
% k=3) classification???
medium
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{PROP-G} &
% The authors show that an Internet-like underlying physical topology has much
% better performance
medium &
% Exchanging neighbours within a radius of 2 (TTL value) reduces stretch
% significantly, while keeping the additional overhead at very reasonable levels
low &
% The effectiveness of the scheme is reduced while the system size becomes
% larger, but as the number grows, this reduction becomes smaller
medium \\
\emph{PROP-O} &
% The algorithm can better reclaim the heterogenity of peers (those with faster
% response) to reduce the system's aggregate delay. 
medium &
% Same as above
medium &
% The queries are directed through fast nodes so it is important such nodes
% be part of the network
medium \\
\end{tabular}
\end{center}

% TODO: SOME DISCUSSION
% PROP-G can be applied to both structured and unstructured overlays.

@@

% TODO: CHECK ONCE AGAIN
\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
? &
%
? &
%
?
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Clustering approaches reduce search scope (or at least increase search
% satisfaction time). The algorithm tries to ease this problem by allowing some
% connections to be random
medium &
% overhead of split-hash and dnMatch is of low cost (TODO: double check this).
% Walker message is multicasted only when sibling connections must be
% established.
low &
% it can be utilised in hierarchical architectures as well meaning increased
% scalability. Tests show that an increase from 5K- to 10K-node system slightly
% increases the average hops needed to satisfy a lookupDN message.
medium
\end{tabular}
\end{center}
